### 2018-01-24 includes/problems.tex
Fixing typos and descriptions.

    The \texttt{transformerd} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:

>>>>

    The \texttt{transformed} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:

### 2018-01-24 includes/stringfuzz.tex
Fixing typos and descriptions.

            \begin{tabular}{|l|l|}
                \hline
                \textbf{Name} & \textbf{Generated Problems have ...} \\ \hline
                concats       & Long concats and optional random extracts. \\ \hline
                lengths       & Many variables (and their concats) with length constraints. \\ \hline
                overlaps      & An expression of the form A.X = X.B. \\ \hline
                equality      & An equality among concats, each with variables or constants. \\ \hline
                regex         & Regexes of variying complexity. \\ \hline
                random-text   & Random, likely syntactically invalid text. \\ \hline
                random-ast    & Totally random, but semantically valid text. \\ \hline
            \end{tabular}

@@

            \begin{tabular}{|l|l|}
                \hline
                \textbf{Name} & \textbf{The transformer ...} \\ \hline
                fuzz          & Randomly replaces literals and operators with similar ones. \\ \hline
                graft         & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
                multiply      & Multiplies each number by N, and repeats each character N times. \\ \hline
                nop           & Does nothing. \\ \hline
                reverse       & Reverses all string literals and concat arguments. \\ \hline
                rotate        & Performs a random concat tree rotation. \\ \hline
                translate     & Maps every character X to a different character Y. \\ \hline
                unprintable   & Replaces all characters with unprintable ones. \\ \hline
            \end{tabular}

@@

        \fuzzer{} can generate and transform problems with regular expression constratints. The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output. It generates a problem in the form\footnote{Variable declarations omitted for brevity.}:

@@

        \fuzzer{} can be used to generate static benchmarks as described in Section~\ref{sec:problems}. It cna also be used in a randomised fashion for exploratory debugging. As a motivating example, the following usage can feed random problems to \cvc{} until it returns an error:

>>>>

            \begin{tabular}{|l|l|}
                \hline
                \textbf{Name} & \textbf{Generated Problems have ...} \\ \hline
                concats       & Long concats and optional random extracts. \\ \hline
                lengths       & Many variables (and their concats) with length constraints. \\ \hline
                overlaps      & An expression of the form A.X = X.B. \\ \hline
                equality      & An equality among concats, each with variables or constants. \\ \hline
                regex         & Regexes of varying complexity. \\ \hline
                random-text   & Random, likely syntactically \textit{in}valid text. \\ \hline
                random-ast    & Random, but semantically \textit{valid} text. \\ \hline
            \end{tabular}

@@

            \begin{tabular}{|l|l|}
                \hline
                \textbf{Name} & \textbf{The transformer ...} \\ \hline
                fuzz          & Randomly replaces literals and operators with similar ones. \\ \hline
                graft         & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
                multiply      & Multiplies each number by N, and repeats each character N times. \\ \hline
                nop           & Does nothing. \\ \hline
                reverse       & Reverses all string literals and concat arguments. \\ \hline
                rotate        & Performs a random syntax tree rotation on two concats. \\ \hline
                translate     & Maps every character X to a different character Y. \\ \hline
                unprintable   & Randomly replaces all characters in literals with unprintable ones. \\ \hline
            \end{tabular}

@@

        \fuzzer{} can generate and transform problems with regular expression constraints. The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output. It generates a problem in the form\footnote{Variable declarations omitted for brevity.}:

@@

        \fuzzer{} can be used to generate static benchmarks as described in Section~\ref{sec:problems}. It can also be used in a randomised fashion for exploratory debugging. As a motivating example, the following usage can feed random problems to \cvc{} until it returns an error:
